True versus apparent shapes of astrophysical bow shocks

### 2016-05-12 papers/Paper1/sec-application.tex
Tidy up the text (a bit) and inserted new figures

--- Rethink if should be included on paper ---
Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).

\begin{figure*}
\begin{tabular}{ccc}
\includegraphics[width=0.35\linewidth]{R0-b}&
\includegraphics[width=0.35\linewidth]{Rc-b} &
\includegraphics[width=0.35\linewidth]{R90-b}
\end{tabular}
\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \CRW{}
are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
\label{fig:rad-beta}
\end{figure*}

--- Finished rethinking ---
Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

Although there is an analytical form for the radius of curvature, for $i\ne 0$ there is not an intuitive form for  $R'_c$. Plus, in practice, we are working with discret arrays, so, when transforming the shell's coordinates to the primed system, we almost certainly will miss the $\theta'=0$ point, which
should allow us to estimate the radii $(R'_0,R'_c)$, the first with equation (\ref{eq:Rpar}) and the second with the mathematical definition of the radius of curvature using the primed coordinates. Insted, we estimate $R'_0$ as the projected radius with the value of $\theta'$ closest to zero, and
$R'_c$ doing a least square fit to the points such as $\theta' \leq 45^\circ$. This restriction allows to obtain the best estimation of the radius of curvature at the nos of the shell. A lower cuttoff may undestimate $R'_c$ while higher cutoffs might be unaccurate, too.

@@

\subsection{Conic Scenario}

Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
momenta and different density distributions. 
In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
LV4 is a special case which fits better with an hyperbola and isotropic wind.

>>>>

finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)

\begin{figure*}
\begin{tabular}{ccc}
\includegraphics[width=0.35\linewidth]{A-beta}&
\includegraphics[width=0.35\linewidth]{B-beta} &
\includegraphics[width=0.35\linewidth]{thc-beta}
\end{tabular}
\caption{$\theta_c$, $R_c$ and $R_{90}$ versus $\beta$ for different anisotropy degrees, represented with the $\xi$ paramenter.}
\label{fig:rad-beta}
\end{figure*}

%Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds 
momenta and different density distributions.

In figure (\ref{fig:conic-xi}) we show the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$. Most of the proplyds fit well 
with a elliptic-like conic shape and moderate to high degree of anisotropy of their wind.
LV4 is a special case which fits better with an hyperbola and isotropic wind.

%Although there is an analytical form for the radius of curvature, for $i\ne 0$ there is not an intuitive form for  $R'_c$. Plus, in practice, we are working with discret arrays, so, when transforming the shell's coordinates to the primed system, we almost certainly will miss the $\theta'=0$ point, which
%should allow us to estimate the radii $(R'_0,R'_c)$, the first with equation (\ref{eq:Rpar}) and the second with the mathematical definition of the radius of curvature using the primed coordinates. Insted, we estimate $R'_0$ as the projected radius with the value of $\theta'$ closest to zero, and
%$R'_c$ doing a least square fit to the points such as $\theta' \leq 45^\circ$. This restriction allows to obtain the best estimation of the radius of curvature at the nos of the shell. A lower cuttoff may undestimate $R'_c$ while higher cutoffs might be unaccurate, too.

@@

%\subsection{Conic Scenario}
